Stack Safety as a Security Property

### 2020-07-10 main.tex
Remove token appendix
Nit in 5

Consider the result of modifying line 42 of our running example to $r_4 \leftarrow [\rsp - 9]$.
Instead of reading the proper argument {\tt v}, {\tt h} now reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in {\high} and low confidentiality in {\low}. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but all other addresses
hold -5, in {\varied}.  After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in light {\low}, and while 109
had changed in a consistent way (independent of the variation), 108 holds either 43 or -4, so the trace does not obey trace confidentiality.
%\rb{Color name macros}
%\apt{Explain slash notation in effects column.}
%\rb{Wrote some words to explain after def. 5.4 (variations).}

@@

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

Consider the result of modifying line 42 of our running example to $r_4 \leftarrow [\rsp - 9]$.
Instead of reading the proper argument {\tt v}, {\tt h} now reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in {\high} and low confidentiality in {\low}. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but all other addresses
hold $-5$, in {\varied}.  After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in light {\low}, and while 109
had changed in a consistent way (independent of the variation), 108 holds either 43 or $-4$, so the trace does not obey trace confidentiality.
%\rb{Color name macros}
%\apt{Explain slash notation in effects column.}
%\rb{Wrote some words to explain after def. 5.4 (variations).}

@@

%% Appendix
%\appendix
%\section{Appendix}
%Text of appendix \ldots
